---
title: "centralDogma"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{centralDogma}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(centralDogma)
```

# Brief description of the use of this package  
The package works much like a logo-plot, but much simpler. Converts a DNA-string to an amino acid sequence, and plots their respective frequencies.  

Notice that each function is demonstrated using the output from the previous function.  

# Examples of each function  
## create_random_dna_seq  
\code{create_random_dna_seq} takes as an argument an integer, and returns a randomly generated DNA-sequence of that length:  
```{r}
(dna_seq <- create_random_dna_seq(15))
```

## convert_dna_to_rna  
\code{convert_dna_to_rna} takes as an argument a DNA-sequence, and returns a RNA-sequence:  
```{r}
(rna_seq <- convert_dna_to_rna(dna_seq))
```

## codon_iden
\code{codon_iden} splits the RNA-sequence into codons as below:  
```{r}
(codons <- codon_iden(rna_seq))
```